Measuring background risk and systemic risk in finance

### 2015-05-29 srisk3.tex
pdj changes

The right hand side of \eref{formula} splits the stressed expectation $\Es(p_{it})$ into two components: 
\be{vsstress}
\Es(p_{it}) =\mu_{it}+s_{it}\cq 
 \mu_{it} \equiv \E(p_{it})=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \ ,
\ee
$$
s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\ , 
$$
called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$.  Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.

@@

Writing  $\sigma_{\phi}$ as the standard deviation of $\phi$,  define the systemic beta of firm $i$ with respect to stress $\phi$ as
\be{zscore}
\beta_{it}\equiv \frac{s_{it}}{\sigma_\phi}
\ee
where  $\sigma_\phi$ is the standard deviation of $\phi$.   Thus $\beta_{it}$ is the systemic stress component in \eref{formula} standardised by $\sigma_\phi$ and
\be{zscore2}
\E_s(\phi)  = \mu_{it} + \beta_{it}\sigma_\phi\cq \E(p_{it}|\phi) \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ .
\ee
The second, approximate, relationship is suggested from   $\cov(p_{it},\phi)/\sigma^2_\phi$ analogous to the regression coefficient of $p_{it}$ on $\phi$.

>>>>

The right hand side of \eref{formula} splits the stressed expectation $\Es(p_{it})$ into two components: 
\be{vsstress}
\Es(p_{it}) =\mu_{it}+s_{it}\cq 
 \mu_{it} \equiv \E(p_{it})=q_{it}\E(p_{it}|\nu_{it}\le \ell_{it}) \ ,
\ee
$$
s_{it} \equiv \cov\{\E(p_{it}|\phi),\phi\}\ , 
$$
called  the background stress  and systemic stress, respectively, in firm $i$ at time $t$.  Since both $\Es(p_{it})$ and $\E(p_{it})$ lie between 0 and 1 it follows both $\mu_{it}$ and $s_{it}$ lie between 0 and 1 and  are loosely interpreted as probabilities.  Further note 
$$
\E(p_{it}|\nu_{it}\le \ell_{it}) \approx \ell_{it}-\E(\nu_{it}|\nu_{it}\le \ell_{it})\ .
$$
(Weihao, do you think it is worthwhile to decompose the $s_{it}$ analogously in terms of a probability time a tail event?)

@@

Writing  $\sigma_{\phi}$ as the standard deviation of $\phi$,  define the systemic beta of firm $i$ with respect to stress $\phi$ as
\be{zscore}
\beta_{it}\equiv \frac{s_{it}}{\sigma_\phi}
\ee
where  $\sigma_\phi$ is the standard deviation of $\phi$.   Thus $\beta_{it}$ is the systemic stress component in \eref{formula} standardised by $\sigma_\phi$ and
\be{zscore2}
\Es(p_{it})  = \mu_{it} + \beta_{it}\sigma_\phi\cq \E(p_{it}|\phi) \approx \mu_{it} + \beta_{it}\frac{\phi-1}{\sigma_\phi}\ .
\ee
The second, approximate, relationship is suggested from   $\cov(p_{it},\phi)/\sigma^2_\phi$ analogous to the regression coefficient of $p_{it}$ on $\phi$.
